\documentclass{article}
\usepackage{geometry}
\geometry{
    top=0.5in,
    left=1in,
    right=1in,
    bottom=1in
}

\title{\textbf{SkillVine} \\ \large -An online platform for managing, evaluating & grading activity points.}
\author{}
\date{}

\begin{document}

\maketitle

{\centering\textbf{\Large Abstract}\par}

\bigskip

\Large Our web-based Activity Points Management System is a much-needed
solution that simplifies and enhances the way student certificates for activity
points allocation are handled. The system integrates and automates the
existing process of uploading, evaluating and awarding certificates. It saves
time and resources for both students and teachers by eliminating paper-based
certification and manual verification procedures. The system also verifies the
authenticity of certificates and provides feedback on their validity and
maximum points each certificate deserves to the concerned teacher. These
features improve the quality and reliability of the certification process.
\par
\bigskip
\Large Furthermore, our solution offers students a unified platform for storing and
organising their certificates in an online portal, improving their productivity
and accuracy. It increases student engagement and motivation by providing
them with instant feedback and recognition for their achievements. Our
system is designed to be user-friendly, secure and scalable. It can be accessed
from any device with an internet connection. Our system aims to provide a
convenient, efficient and transparent way of managing student activity points.

\bigskip

{\large\textbf{Project Members:}}

Alvin Varghese

Anson Anthrayose Thomas

Sreerag M

Vignesh R Pillai

\bigskip

{\large\textbf{Project Guide:}}

Asst. Professor Aswathy B

\end{document}
