\section{Connectivity algorithm}

\begin{frame}

 \frametitle{\centering Module-2}
    \framesubtitle{Connectivity Algorihtms}

        \begin{itemize}
            \item Student Login algo
            \item Teacher Login algo
            \item Student Dashboard algo
            \item Certificate Add algo
            \item Certificate view(Teacher and Student) algo
            \item Report generating algo
        \end{itemize}
 
\end{frame}


\begin{frame}{Student Login}
    \framesubtitle{Connectivity Algorithm}
        \begin{enumerate}
\item User selects "Login as student".
\item Student logs in with their institution email.
\item Client sends request to server at api/auth/students/.
\item Server checks if student exists in database. If not, redirect student to a data collection form to enter admission number, KTU ID, and name. Server updates student collection in database.
\item Server generates access token for student.
\item Server redirects student to dashboard using access token for subsequent requests.
        \end{enumerate}
    
\end{frame}

\begin{frame}{Teacher Login}
    \framesubtitle{Connectivity Algorithm}
        \begin{enumerate}            
\item User selects "Login as teacher".
\item Teacher logs in with their institution email.
\item Client sends request to server at api/auth/teacher.
\item Server checks if teacher exists in database. If not, create teacher in collection.
\item Server generates access token for teacher.
\item Server redirects teacher to student select page using access token for subsequent requests.
        \end{enumerate}
    
\end{frame}


\begin{frame}{Student Dashboard}
    \framesubtitle{Connectivity algorithm}
    \begin{enumerate}
        

\item Student logs in and is redirected to dashboard.
\item Client sends GET request to server for notifications at api/students/notifications.
\item Client displays notifications on the notification panel.
\item Sidebar displays button to fetch student's current activity points.
\item Client sends GET request to server at api/students/score and displays score in sidebar.
\item Student can navigate to all pages from navbar on the left.
    \end{enumerate}
\end{frame}

\begin{frame}{Teacher Dashboard}
    \framesubtitle{Connectivity Algorithm}
    \begin{enumerate}
        
\item Teacher logs in and is redirected to dashboard.
\item Client sends GET request to server for all batches in database at api/batches.
\item Client displays all batches on UI.
\item Teacher selects a batch.
\item Client sends GET request to server for all students in that batch at api/batches/{batchID}.
\item Teacher selects a student.
\item Client sends GET request to server for all certificates of that student at api/certificates/{studentID}.
\item Client displays a page where all certificates are listed year-wise.
    \end{enumerate}
    
\end{frame}

\begin{frame}{Add Certificate}
    \framesubtitle{Connectivity Algorithm}
        \begin{enumerate}
            

\item Student selects "Add Certificate" from dashboard.
\item Client sends GET request to server to fetch all available activities and categories of events.
\item  Client displays available activities, categories of certificates in dropdown menus for student to select from.
\item  Student selects certificate to add and enters required fields: student ID, certificate name, description, date, and any additional information.
\item Client sends new certificate data as POST request to server at api/certificates.
\item  Server updates student's certificate collection with new certificate.
\item  Server sends response to client indicating success or failure of certificate addition.
        \end{enumerate}
    
\end{frame}

\begin{frame}{View Certificate}
    \framesubtitle{Connectivity Algorithm}
    \begin{enumerate}

\item Student or teacher navigates to the certificates page.
\item User clicks on a certificate.
\item If specific certificate is selected, client sends GET request to server for certificate details at api/certificates/{certificateID}.
\item  Server returns details of selected certificate.
\item  Client displays selected certificate's details on separate page.
    \end{enumerate}
    
\end{frame}

\begin{frame}{Report generation}
\framesubtitle{Connectivity Algorithm}
    \begin{enumerate}
        

\item Teacher navigates to report generation page.
\item Client sends GET request to server to fetch all available batches at api/batches.
\item Server returns all available batches.
\item Client displays all batches in dropdown menu for teacher to select from.
\item Teacher selects a batch.
\item If teacher clicks on "Generate Report":
    \begin{enumerate}
       
    
   \item Client sends GET request to server to fetch details for selected batch at api/reports/batches/{batchID}.
   \item Client generates report based on data sent from server and creates PDF report.
    \item Client displays generated report on separate PDF page and allows download.
    \end{enumerate}
\item  Else the client sends a GET request to server to fetch students at api/batches/{batchID}.
\begin{enumerate}
     

   \item The client displays all students in a dropdown menu for the teacher to select from.
 \item If teacher clicks on generate report here,
   \item The client sends a GET request to server to fetch details for the selected student at api/reports/students/{studentID}.
    \item The client generates the report based on the data sent from server and makes a PDF report.
    \item The client displays the generated report on a separate PDF page and can download if they want.
    \end{enumerate}
    \end{enumerate}
    
\end{frame}